---
title: "GapMinder Analysis"
author: "Magdalena Woińska"
date: "March 11, 2019"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
---

- # Introduction

Here is my first RMarkdown document!

- # Let's embed some R code.

We'll writ e on R chunk here that loads the tidyverse library and then reads in the GapMinder dataset from our project directory.

```{r}
library(tidyverse)
gm <- read_csv("gapminder.csv")
```


# investigate gm

Let's look at the gm dataset

```{r}
head(gm)
```

- # Our first plot

Showing the gdp per capita on the x axis and the life expectancy on the y

```{r}
library(ggplot2)
ggplot(gm,aes(gdp_per_cap,lifeexp)) + geom_point()
```

- # A better plot

Adding color by continent and adding a log scale for gdp

```{r,fig.cap="Life Expectancy by GDP",echo=FALSE}
ggplot(gm,aes(gdp_per_cap,lifeexp))+
  scale_x_log10()+
  geom_point(aes(col=continent))
```


- # Trying out a kable table

Same datat using

```{r}
head(gm)
```

head as a table
```{r}
library(knitr)
kable(head(gm))
```

